{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Meeting State

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$. {\color{orange} May we put the link to the figure 4 by footnote?} These measurement points can be different for each sample curve. However, in this paper, we only consider the case where curves share their measuring points.
	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure. Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\

	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis. One example of i.i.d. curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d. random process itself.

@@

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper {\color{orange} link with specify?} are explained in the following. {\color{orange}or Each unique feature of the basis systems is used to interpret results of simulation study and application of this study. with link} Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.

	\paragraph{Monomial Basis}
	A very simple idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis. For entire functions $f(t)$, e.g. polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

@@

	\paragraph{Fourier Basis}
	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions. Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

@@

	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values. The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process. Additionally, the Fourier basis is especially suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions. {\color{red} Citation}
	\vspace{-0.2cm}

@@

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  {\color{orange} The theoretical progress is also precisely shown at one eqution(link).} $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.

@@

	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process. {\color{orange} Moreover, our data generating process is also based on this property.}\\

@@

	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. {\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability (cf. \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf. \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

@@

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a  cubic B-spline basis which is created using 50 knots. In the R implementation of the fda package, these 50 knots account for 52 basis functions (50+4-2). These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}_{1},\: \dots \:, \mathring{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$. Finally, we obtain the generated curves $NIR_{sim}$ as

@@

		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations, using the two true coefficient functions and the two error terms. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification. The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

@@

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in the appendix. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR. Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence: It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$. An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the higher noise responses. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise into $\hat{\beta}(t)$. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval.	\\

	\subsubsection{Functional Principal Component Regression}
		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSPE is decreasing in the increasing number of FPC's and chosen basis functions for both the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the chosen basis functions. The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the MSPE suggests better models with a higher number of FPC's. While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$. In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of over-fitting using $n_{FPC} = 4$. Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4 ,6 ,23 for $n_{FPC} \in \{2, 3, 4 \}$)
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$. $f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$. Both configurations of $f_2$ are using 5, 15, 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
	\vspace{-0.2cm}

	\subsubsection{Interpretation and Relevance for Application}
	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with lower $L$. This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$. The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture in our setting. To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX). As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there exists a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower than for 70 basis functions which might be a first sign of a too high $K$ and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better on a lower truncated smoothed curve (here $L = 50$). Importantly, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ration of the responses is not affecting the construction of the FPC's which might indicate benefiting attributes of the lower basis functions used in the main simulation.

@@

	\paragraph{Larger Range for the Number of Basis Functions for FPCR}
	\vspace{-0.2cm}

	\paragraph{Larger Range for the Number of Principal Components}
	\vspace{-0.2cm}

@@

	\newpage
	\subsection{Simulation - Coefficient Function Estimates}

@@

	\section*{Affidavit}

>>>>

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$.  These measurement points can be different for each sample curve. However, in this paper, we only consider the case where curves share their measuring points.
	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure. Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\

	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis. One example of i.i.d. curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d. random process itself. More information about this example can be found in Appendix \ref{NIR}.

@@

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A very simple idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis. For entire functions $f(t)$, e.g. polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

@@

	\paragraph{Fourier Basis}
	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions. Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_i \cos(2\pi i x - \phi_i) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

@@

	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values. The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process. The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions. (cf. \cite{ramsay_functional_2005})
	\vspace{-0.2cm}

@@

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations. $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.

@@

	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process. Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\

@@

	The parameter $M \in \{1,\: \dots \:, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf. \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf. \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

@@

	\subsection{Generating Similar Curves}\label{similar_curves}
	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a  cubic B-spline basis which is created using 50 knots. In the R implementation of the fda package, these 50 knots account for 52 basis functions ($50+4-2$). These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}^{1},\: \dots \:, \mathring{\xi}^{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}^1,\: \dots\:, \hat{\lambda}^M))$. Finally, we obtain the generated curves $NIR_{sim}$ as

@@

		 Two different error-terms $\epsilon$ were created by first generating an i.i.d. standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations, using the two true coefficient functions and the two error terms. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification. The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} & =  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} }\mathrm{d}s) 
			    \approx \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

@@

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in Appendix \ref{Tables_sim} and \ref{Estimates_sim}. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR. Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis. It still performs the worst for $f_1$. An explanation might be its exaggerated behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the lower signal-to-noise ratios. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval lending itself to a periodic representation.	\\

	\subsubsection{Functional Principal Component Regression}
		The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions. The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the MSPE suggests that models with a higher number of FPC's perform better. While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$. In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting using $n_{FPC} = 4$. Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} \in \{2, 3, 4 \}$)
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$. $f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$. Both configurations of $f_2$ are using 5, 15 and 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
	\vspace{-0.2cm}

	\subsubsection{Interpretation and Relevance for Application}
	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems to be introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$. This results in higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$. The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting. To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX). As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be a first sign of a too high $L$ and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$). The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's which might indicate beneficial attributes of the lower truncation parameters used in the main simulation.

@@

	\paragraph{Larger Range for the Number of Specifications for FPCR}
	\vspace{-0.2cm}

@@

	\newpage
	\subsection{Simulation - Coefficient Function Estimates}\label{Estimates_sim}

@@

	\newpage
	\section*{Affidavit}
